Evaluative adjective sentences: \\ A question-based analysis of projection

### 2019-04-25 paper/paper-anon.tex
Added some comments + fixed small typos

\newcommand{\jt}[1]{\textbf{\color{blue}JT: #1}}
\newcommand{\jd}[1]{\textbf{\color{red}[jd: #1]}}

@@

Two contents of evaluative adjective sentences, like {\em Kim was smart to watch the movie}, are the prejacent (that Kim watched the movie) and the generalization (that the degree to which Kim watching the movie is smart is higher than the contextual standard of {\em smart}). The prejacent is standardly analyzed as a presupposition
(e.g., \citealt{norrick78,barker02,oshima09b,kertz2010}). This paper argues against such \jd{such = what?} analyses because, among other things, they do not capture an interaction between the prejacent and the generalization that has not yet been observed for projective content: when the prejacent projects, the generalization does not, and when the prejacent does not project, the generalization does \jd{does the evidence really favor such categorical a view?}. We develop an analysis according to which the prejacent is not a lexically specified presupposition but projects if it is not at-issue with respect to the question addressed by the utterance of the evaluative adjective sentence . In addition to capturing the interaction between the prejacent and the generalization, our question-based projection analysis significantly expands on previous such analyses (e.g., \citealt{beaver-clark08,best-question,brst-ar,abrusan2011}) by incorporating a novel constraint on the question addressed by an utterance: the more the truth of an utterance content follows from the common ground \jd{can something follow more or less, or should this instead be "the more likely the truth of an utterance content is to follow from the common ground..."}, the less likely the question is about that content. We provide experimental evidence for the proposed analysis and argue that our analysis improves on that of \citealt{karttunen-etal2014}, according to which evaluative adjectives are systematically ambiguous.

@@

Recently, \citet{karttunen-etal2014} provided naturally occurring examples that show that utterances of sentences in which the evaluative adjective is embedded under negation can receive an interpretation according to which the prejacent
does not project, but is interpreted in the scope of negation. For instance, the speaker of (\ref{nat}a) is not committed to living close to their parents and instead communicates that they do not live close to their parents. Likewise, the speaker of (\ref{nat}b) is not committed to having stumbled through the junkyard in the dark but rather communicates that they did not stumble through the junkyard.

@@

To account for examples like (\ref{nat}), in which the prejacent is not a commitment of the speaker, presupposition analyses appeal to local accommodation, a process whereby a presupposition is added to a local context, such as the context created by negation: presuppositions can be locally accommodated if adding the presupposition to the common ground of the interlocutors (a process known as global accommodation) would result in a contradiction, uninformativity or problems with
binding (\citealt{heim82,vds92}). In example (\ref{nat}a), for instance, the prejacent is locally accommodated under negation because globally accommodating the prejacent in the common ground would result in a contradiction: the prejacent is that the speaker lived close to their parents, but, according to the context, the closest that the speaker lived to their parents was when the speaker lived in Denver, Colorado, i.e., about 300 miles (480 km) away from their parents in Garden City, Kansas. The prejacent is correctly predicted to be locally accommodated in (\ref{nat}a), i.e., does not become a commitment of the speaker.

Negated evaluative adjective sentences (NEASs) like (\ref{nat}) point to two problems for analyses according to which the prejacent is a presupposition. The first problem concerns the prejacent. In example (\ref{nat}b), globally accommodating the prejacent does not result in a contradiction, uninformativity or problems with
binding: if the prejacent was added to the common ground,
(\ref{nat}b) would mean that the speaker knew that someone was in the
junkyard, that they stumbled through the junkyard and got hurt, and that
the speaker does not consider these actions stupid (perhaps because these actions
led to the person in the junkyard receiving help). Because such an interpretation does not result in a contradiction, uninformativity or problems with
binding, analyses that take the prejacent to be a presupposition incorrectly  predict that the prejacent of (\ref{nat}b) is globally accommodated, i.e., is a commitment of the speaker.\footnote{It may be possible to account for the non-projection of the prejacent on the basis of plausibility considerations: \citealt[162]{vonfintel08}, for instance,  proposed that ``what gets accommodated depends on the best guess of the hearers about what the speaker might have intended as the adjustment to the common ground that would admit the asserted sentence''. The cues to the projectivity of the prejacent identified in the following sections may help flesh out the reasoning process that hearers and readers undergo in interpreting EASs. Plausibility considerations do not, however, address the second problem that presuppositional analyses face.}

@@

However, there are also concerns with Karttunen et al.'s analysis. Because it is not formalized, it is not clear that it makes correct predictions about content other than the prejacent. According to the lexical entry in (\ref{lex}a), what is asserted is that it is not the case that for Feynman to dance on the table would be stupid: \citet[248]{karttunen-etal2014} assume that from this asserted content and the presupposed prejacent that it is not the case that Feynman dancing on the table was stupid. According to the lexical entry in (\ref{lex}b), what is asserted is that it is not the case that what the speaker did about stumbling through the junkyard was stupid. That the prejacent is negated (the speaker didn't stumble through the junkyard) follows, according to \citealt[249]{karttunen-etal2014}, from what is presupposed and what is asserted. Another concern is that Karttunen et al.'s analysis comes at a high cost: to derive the two interpretations, evaluative adjectives are systematically ambiguous. In addition to hardwiring the projection of the prejacent into one lexical entry but not the other, the analysis also hardwires the interaction between the projection of the prejacent and the generalization, which  would preferably fall out from a projection analysis.

@@

In this section, we develop a question-based projection analysis for EASs.\footnote{This is not to suggest that lexicalist projection analyses are never appropriate: we assume, for instance, that contents associated with what \citealt{brst-lang11} refer to as a Strong Contextual Felicity constraint are lexically specified presuppositions and that the projection of conventional implicatures is best attributed to conventional specification (e.g., \citealt{potts05,murray2014}. For discussion  see AUTHORS 2013, 2018, 2019.
%\citealt{brst-lang11,tbd-variability,tonhauser-etal-sub26}.
} In section \ref{s21}, we introduce relevant aspects of the question-based projection analysis developed in \citealt{best-question}. In section \ref{s22}, we show that the prejacent and the generalization are lexical entailments of EAS and that, furthermore, exactly one of them is at-issue in any given utterance; this predicts the interaction in the projection of these two contents. In section \ref{s23}, we expand on previous question-based projection analyses by incorporating a constraint on the questions addressed by utterances of EASs.

@@

\end{xlist}
\end{exe}
In sum, under \citepos{best-question} proposal, utterance content may project if it is not at-issue with respect to the Discourse Question addressed by the utterance. The question of why not-at-issue content projects has received several different answers. \citet{potts05} assumed that it was due to such content being contributed to a separate dimension of meaning, and \citet{brst-salt10} proposed that not-at-issue content is not targeted by operators, such as negation, thereby resulting in the content projecting over such operators. In this paper, we follow \citealt{abrusan2011,abrusan2016} in assuming that the not-at-issue content is backgrounded and projects as a result of its discourse status.\footnote{We do not otherwise follow Abrus\'an's analysis of which content is backgrounded because it, unfortunately, does not appear to make correct predictions for EAS. \citet{abrusan2011} proposed that entailments of utterances that are about the running time of the main event are the default main point, i.e., what we have referred to as the at-issue content. This analysis, however, does not make correct predictions for EAS: given Abrus\'an's notion of aboutness, both the prejacent and the generalization of EASs are about the running time of the main event. For instance, \citet[508]{abrusan2011} took the entailment of (i), that John solved the exercise, to be ``non-accidentally (i.e. necessarily) about the matrix event time''. By the same argument, the prejacent of (ii) would be about the matrix event time, which means that neither the prejacent nor the generalization are predicted by \citealt{abrusan2011} to be the default at-issue content of EASs.

@@

Having motivated that both the prejacent and the generalization are lexical entailments of EAS, we now turn to the discourse status of these contents. The discourse status of the prejacent and the generalization is not conventionally specified by the EAS: both can be entailed by the common ground at the time at which the utterance is made or new information at the time at which the EAS is uttered (in other words, neither content is associated with what \citealt{brst-lang11} call a Strong Contextual Felicity constraint). To illustrate, consider the naturally occurring EASs in (\ref{new}). The EAS in (\ref{new}a) is acceptable in a context in which the prejacent follows from the common ground, i.e., the interlocutors already know that Trump gave Wolff unlimited access, and in which the speaker conveys the generalization as new information, i.e., that she considers the degree to which events of Trump giving Wolff unlimited access are stupid is higher than the contextual standard of {\em stupid}. The EAS in (\ref{new}b) illustrates that the discourse status of the prejacent and the generalization can also be reversed: (\ref{new}b) is acceptable in a context in which the generalization follows from the common ground, whereas the prejacent, that MacLean grabbed Kouassi in his private parts is new information. And, finally, there are also EAS in which both the prejacent and the generalization may be new information: (\ref{new}c) is acceptable in a context in which neither the generalization nor the prejacent follow from the common ground. When a speaker utters the EAS in (\ref{new}c), the speaker may be thereby committing to the truth of the prejacent, that they bought an Xbox, to the truth of the generalization, that the degree to which events of them buying an Xbox 360 elite are stupid is higher than the contextual standard of {\em stupid}.

@@

Not only can both the prejacent and the generalization of an EAS be new information, they can also both be at-issue with respect to the Discourse Question addressed by an utterance of the EAS. Of course, it follows from the characterization of at-issue content as addressing the Discourse Question that only one of them is at-issue in any given utterance of an EAS. We further assume that the prejacent and the generalization are the only contenders for at-issue content of an EAS, which means that exactly one of them is at-issue in any given utterance of an EAS, the other one is not-at-issue.\footnote{As discussed in detail in \citealt[\S4.2]{barker02}, EAS also give rise to subject-related entailments, namely that the denotation of the subject noun phrase is capable of volition and, regarding the situation described by the {\em to-}infinitive, has the power to bring it about and intends for it to come about. We follow \citealt{barker02} in assuming that these entailments are lexically-specified presuppositions. Consequently, these entailments are conventionally specified as not at-issue.} To illustrate, consider the examples in (\ref{ai}), in which utterances of the same EAS address four distinct Discourse Questions. The Discourse Questions in (\ref{ai}a) and (\ref{ai}b) are about the prejacent: both the question of whether Sam got a ticket in (\ref{ai}a) and who got a ticket in (\ref{ai}b) are answered by the prejacent of B's utterances, that Sam got a ticket.\footnote{Some native speakers of American English would prefer to produce B's utterances in (\ref{ai}a) and (\ref{ai}b) with {\em enough}: {\em She was smart enough to buy one the day they went on sale}. We hypothesize that such speakers disprefer producing EAS in which the prejacent is at-issue. Given our hypothesis that the prejacent projects when it is not at-issue, we would expect such speakers to also disprefer producing NEAS like (\ref{nat}) in which the prejacent does not project. Crucially, as discussed in section \ref{s1}, even speakers who prefer to produce (\ref{ai}a) and (\ref{ai}b) with {\em enough} can retrieve the intended interpretations of the variants without {\em enough}.} Thus, in (\ref{ai}a) and (\ref{ai}b), the prejacent is at-issue and the generalization, that the degree to which events of Sam buying a ticket the day the tickets went on sale are stupid is higher than the contextual standard of {\em stupid} is not at-issue. The Discourse Questions in (\ref{ai}c) and (\ref{ai}d), on the other hand, are not about the prejacent:  neither the question about B's assessment of events of Sam buying a ticket they went on sale (\ref{ai}c) nor the question of whether Sam was smart to buy a ticket the day they went on sale in (\ref{ai}d) are answered by the prejacent of B's utterances; rather they are answered by the generalization. Thus, in (\ref{ai}c) and (\ref{ai}d), the generalization is at-issue and the prejacent is not at-issue.

@@

\ex Jane saw a man with a gun. She wasn't smart to call the police. 
\end{xlist}
\end{exe}
To assess the projectivity of the prejacent, participants were asked whether the prejacent is true, e.g., `Did Sue lose her wallet?' in (\ref{cont}a), `Did Sue speak some French' in (\ref{cont}b), and `Did Jane call the police?' in (\ref{context}a) and (\ref{context}b).\footnote{This diagnostic for projectivity differs from the `certain that' diagnostic used in the web-based corpus study or in AUTHORS 2018. Exp.~1 relied on a different diagnostic because it was run before the `certain that' diagnostic was developed. Under the assumption that participants only take the prejacent to be true if it follows from the two-sentence discourse, i.e., if the author of the two-sentence discourse is committed to the prejacent, we take the two diagnostics to be comparable in diagnosing projectivity. See AUTHORS 2018 for a discussion of additional diagnostics for projectivity.}

@@

Participants were told that they would read short descriptions of scenarios and were asked a question about each scenario. They were randomly assigned to a list and presented with the 16 stimuli, one after the other, in random order. They gave their response to the polar question on 7-point Likert scale labeled at four points: No/1, Possibly
no/3, Possibly yes/5, Yes/7, as shown in Figure \ref{f-trial-exp1}.

@@

\paragraph{Data exclusion} The data from 5 participants who did not self-identify as native speakers of American English were excluded. 13 participants gave a response lower than 5/possibly yes to at least one of the control stimuli in (\ref{control-exp1}a-c) or higher than 3/possibly no to at least one of the control stimuli in (\ref{control-exp1}d-f). Their data  were also excluded, leaving data from 134 participants (ages: 18-69; mean age: 33).

@@

The target stimuli consisted of 6 pairs of three-sentence discourses like (\ref{jenny}) for each of the 10 evaluative adjectives explored in the experiments reported on in the main body of the paper, for a total of 60 pairs of target stimuli. The full set of target stimuli is provided in the GitHub repository mentioned in footnote \ref{f-git}. The 120 target stimuli were distributed across 12 lists of 10 stimuli each so that each adjective occurred only once per list, and each list included 5 NEASs and 5 variants with {\em enough}.

@@

\begin{enumerate}[topsep=0pt,itemsep=-4pt]

@@

\begin{enumerate}[topsep=0pt,itemsep=-4pt]

\item[CnT] 	Eve bought a raffle ticket. 	She	wasn't lucky	to win the first prize.
\item[CnT] 	Eve was in a car accident.	She	wasn't lucky	to get away unscathed.
\item[CnT] 	Eve wanted to be a model.	She	wasn't lucky	to have beautiful skin.
\item[CnF] 	Eve wanted to be a model.	She	wasn't lucky	to have bad skin.
\item[CnF] 	Eve bought a raffle ticket. 	She	wasn't lucky	to lose it the next day.
\item[CnF] 	Eve was in a car accident.	She	wasn't lucky	to break her neck.
\item[CxT] 	Eve has a 5th grade education.	She	wasn't lucky	to get a minimum wage job.
\item[CxT] 	Eve was a finalist in The Bachelor.	She	wasn't lucky	to be chosen.
\item[CxT] 	Eve did not understand her chemistry class.	She	wasn't lucky	to get a B.
\item[CxF] 	Eve was the best student in this class.	She	wasn't lucky	to get a B.
\item[CxF] 	Eve was called in for jury duty.	She	wasn't lucky	to be chosen.
\item[CxF] 	Eve has a first rate college education.	She	wasn't lucky	to get a minimum wage job.

>>>>

\newcommand{\jt}[1]{\textbf{\color{blue}JT: #1}}
\newcommand{\jd}[1]{\textbf{\color{red}[jd: #1]}}
\newcommand{\mcdm}[1]{\textbf{\color{teal}[mcdm: #1]}}

@@

Two contents of evaluative adjective sentences, like {\em Kim was smart to watch the movie}, are the prejacent (that Kim watched the movie) and the generalization (that the degree to which Kim watching the movie is smart is higher than the contextual standard of {\em smart}). The prejacent is standardly analyzed as a presupposition
(e.g., \citealt{norrick78,barker02,oshima09b,kertz2010}). This paper argues against such \jd{such = what?} analyses \mcdm{what about ``such an analysis'' or ``analyses which view the prejacent as a presupposition''} because, among other things, they do not capture an interaction between the prejacent and the generalization that has not yet been observed for projective content: when the prejacent projects, the generalization does not, and when the prejacent does not project, the generalization does \jd{does the evidence really favor such categorical a view?}. We develop an analysis according to which the prejacent is not a lexically specified presupposition but projects if it is not at-issue with respect to the question addressed by the utterance of the evaluative adjective sentence . In addition to capturing the interaction between the prejacent and the generalization, our question-based projection analysis significantly expands on previous such analyses (e.g., \citealt{beaver-clark08,best-question,brst-ar,abrusan2011}) by incorporating a novel constraint on the question addressed by an utterance: the more the truth of an utterance content follows from the common ground \jd{can something follow more or less, or should this instead be "the more likely the truth of an utterance content is to follow from the common ground..."}, the less likely the question is about that content. We provide experimental evidence for the proposed analysis and argue that our analysis improves on that of \citealt{karttunen-etal2014}, according to which evaluative adjectives are systematically ambiguous.

@@

Recently, \citet{karttunen-etal2014} provided naturally occurring examples that show that utterances of sentences in which the evaluative adjective is embedded under negation can receive an interpretation according to which the prejacent does not project, but is interpreted in the scope of negation. For instance, the speaker of (\ref{nat}a) is not committed to living close to their parents and instead communicates that they do not live close to their parents. Likewise, the speaker of (\ref{nat}b) is not committed to having stumbled through the junkyard in the dark but \mcdm{why ``but rather''? Isn't ``committed to not p" part of ``not committed to p"?} rather communicates that they did not go stumbling through the junkyard. \mcdm{It seems to me that the reading that they did go is also available. You can easily continue with ``I saved him". So perhaps ``Likewise, the speaker of (\ref{nat}b) can be not committed to having stumbled through the junkyard in the dark, and even communicating that they did not go stumbling through the junkyard.''}

@@

To account for examples like (\ref{nat}), in which the prejacent is not a commitment of the speaker, presupposition analyses appeal to local accommodation, a process whereby a presupposition is added to a local context, such as the context created by negation: presuppositions can be locally accommodated if adding the presupposition to the common ground of the interlocutors (a process known as global accommodation) would result in a contradiction, uninformativity or problems with
binding (\citealt{heim82,vds92}). In example (\ref{nat}a), for instance, the prejacent, that the speaker lived close to their parents, is locally accommodated under negation because globally accommodating the prejacent in the common ground would result in a contradiction: indeed,
%for instance, the prejacent is locally accommodated under negation because globally accommodating the prejacent in the common ground would result in a contradiction: the prejacent is that the speaker lived close to their parents, but, 
according to the context, the closest that the speaker lived to their parents was when the speaker lived in Denver, Colorado, i.e., about 300 miles (480 km) away from their parents in Garden City, Kansas. The prejacent is correctly predicted to be locally accommodated in (\ref{nat}a), i.e., does not become a commitment of the speaker.

Negated evaluative adjective sentences (NEASs) like (\ref{nat}) point to two problems for analyses according to which the prejacent is a presupposition. The first problem concerns the prejacent. In example (\ref{nat}b), globally accommodating the prejacent does not result in a contradiction, uninformativity or problems with binding: if the prejacent, that the speaker went stumbling in the junkyard, was added to the common ground, (\ref{nat}b) would mean that the speaker knew that someone was in the junkyard, that they stumbled through the junkyard and got hurt, and that the speaker does not consider these actions stupid (perhaps because these actions led to the person in the junkyard receiving help). Because such an interpretation does not result in a contradiction, uninformativity or problems with binding, analyses that take the prejacent to be a presupposition incorrectly  predict that the prejacent of (\ref{nat}b) is globally accommodated, i.e., is a commitment of the speaker.\footnote{It may be possible to account for the non-projection of the prejacent on the basis of plausibility considerations: \citealt[162]{vonfintel08}, for instance,  proposed that ``what gets accommodated depends on the best guess of the hearers about what the speaker might have intended as the adjustment to the common ground that would admit the asserted sentence''. The cues to the projectivity of the prejacent identified in the following sections may help flesh out the reasoning process that hearers and readers undergo in interpreting EASs. Plausibility considerations do not, however, address the second problem that presuppositional analyses face.}

@@

However, there are also concerns with Karttunen et al.'s analysis. Because it is not formalized, it is not clear that it makes correct predictions about content other than the prejacent. According to the lexical entry in (\ref{lex}a), what is asserted is that it is not the case that for Feynman to dance on the table would be stupid: \citet[248]{karttunen-etal2014} assume that from this asserted content and the presupposed prejacent it is not the case that Feynman dancing on the table was stupid. According to the lexical entry in (\ref{lex}b), what is asserted is that it is not the case that what the speaker did about stumbling through the junkyard was stupid. That the prejacent is negated (the speaker didn't stumble through the junkyard) follows, according to \citealt[249]{karttunen-etal2014}, from what is presupposed and what is asserted. Another concern is that Karttunen et al.'s analysis comes at a high cost: to derive the two interpretations, evaluative adjectives are systematically ambiguous. In addition to hardwiring the projection of the prejacent into one lexical entry but not the other, the analysis also hardwires the interaction between the projection of the prejacent and the generalization, which  would preferably fall out from a projection analysis.

@@

In this section, we develop a question-based projection analysis for EASs.\footnote{This is not to suggest that lexicalist projection analyses are never appropriate: we assume, for instance, that contents associated with what \citealt{brst-lang11} refer to as a Strong Contextual Felicity constraint are lexically specified presuppositions and that the projection of conventional implicatures is best attributed to conventional specification (e.g., \citealt{potts05,murray2014}). For discussion  see AUTHORS 2013, 2018, 2019.
%\citealt{brst-lang11,tbd-variability,tonhauser-etal-sub26}.
} In section \ref{s21}, we introduce relevant aspects of the question-based projection analysis developed in \citealt{best-question}. In section \ref{s22}, we show that the prejacent and the generalization are lexical entailments of EAS and that, furthermore, exactly one of them is at-issue in any given utterance; this predicts the interaction in the projection of these two contents. In section \ref{s23}, we expand on previous question-based projection analyses by incorporating a constraint on the questions addressed by utterances of EASs.

@@

\end{xlist}
\end{exe}
In sum, under \citepos{best-question} proposal, utterance content may project if it is not at-issue with respect to the Discourse Question addressed by the utterance. The question of why not-at-issue content projects has received several different answers. \citet{potts05} assumed that it was due to such content being contributed to a separate dimension of meaning, and \citet{brst-salt10} proposed that not-at-issue content is not targeted by operators, such as negation, thereby resulting in the content projecting over such operators. In this paper, we follow \citealt{abrusan2011,abrusan2016} in assuming that the not-at-issue content is backgrounded and projects as a result of its discourse status.\footnote{We do not otherwise follow Abrus\'an's analysis of which content is backgrounded because it, unfortunately, does not appear to make correct predictions for EAS. \citet{abrusan2011} proposed that entailments of utterances that are about the running time of the main event are the default main point, i.e., what we have referred to as the at-issue content. This analysis, however, does not make correct predictions for EAS: given Abrus\'an's notion of aboutness, both the prejacent and the generalization of EASs are about the running time of the main event. For instance, \citet[508]{abrusan2011} took the entailment of (i), that John solved the exercise, to be ``non-accidentally (i.e., necessarily) about the matrix event time''. By the same argument, the prejacent of (ii) would be about the matrix event time, which means that neither the prejacent nor the generalization are predicted by \citealt{abrusan2011} to be the default at-issue content of EASs.

@@

Having motivated that both the prejacent and the generalization are lexical entailments of EAS, we now turn to the discourse status of these contents. The discourse status of the prejacent and the generalization is not conventionally specified by the EAS: both can be entailed by the common ground at the time at which the utterance is made or new information at the time at which the EAS is uttered (in other words, neither content is associated with what \citealt{brst-lang11} call a Strong Contextual Felicity constraint). To illustrate, consider the naturally occurring EASs in (\ref{new}). The EAS in (\ref{new}a) is acceptable in a context in which the prejacent follows from the common ground, i.e., the interlocutors already know that Trump gave Wolff unlimited access, and in which the speaker conveys the generalization as new information, i.e., that they consider the degree to which events of Trump giving Wolff unlimited access are stupid is higher than the contextual standard of {\em stupid}. The EAS in (\ref{new}b) illustrates that the discourse status of the prejacent and the generalization can also be reversed: (\ref{new}b) is acceptable in a context in which the generalization follows from the common ground, whereas the prejacent, that MacLean grabbed Kouassi in his private parts is new information. And, finally, there are also EAS in which both the prejacent and the generalization may be new information: (\ref{new}c) is acceptable in a context in which neither the generalization nor the prejacent follow from the common ground. When a speaker utters the EAS in (\ref{new}c), the speaker may be thereby committing to the truth of the prejacent, that they bought an Xbox, to the truth of the generalization, that the degree to which events of them buying an Xbox 360 elite are stupid is higher than the contextual standard of {\em stupid}.

@@

Not only can both the prejacent and the generalization of an EAS be new information, they can also both be at-issue with respect to the Discourse Question addressed by an utterance of the EAS. Of course, it follows from the characterization of at-issue content as addressing the Discourse Question that only one of them is at-issue in any given utterance of an EAS. We further assume that the prejacent and the generalization are the only contenders for at-issue content of an EAS, which means that exactly one of them is at-issue in any given utterance of an EAS, the other one is not-at-issue.\footnote{As discussed in detail in \citealt[\S4.2]{barker02}, EAS also give rise to subject-related entailments, namely that the denotation of the subject noun phrase is capable of volition and, regarding the situation described by the {\em to-}infinitive, has the power to bring it about and intends for it to come about. We follow \citealt{barker02} in assuming that these entailments are lexically-specified presuppositions. Consequently, these entailments are conventionally specified as not at-issue.} To illustrate, consider the examples in (\ref{ai}), in which utterances of the same EAS address four distinct Discourse Questions. The Discourse Questions in (\ref{ai}a) and (\ref{ai}b) are about the prejacent: both the question of whether Sam got a ticket in (\ref{ai}a) and who got a ticket in (\ref{ai}b) are answered by the prejacent of B's utterances, that Sam got a ticket.\footnote{Some native speakers of American English would prefer to produce B's utterances in (\ref{ai}a) and (\ref{ai}b) with {\em enough}: {\em She was smart enough to buy one the day they went on sale}. We hypothesize that such speakers disprefer producing EAS in which the prejacent is at-issue. Given our hypothesis that the prejacent projects when it is not at-issue, we would expect such speakers to also disprefer producing NEAS like (\ref{nat}) in which the prejacent does not project. Crucially, as discussed in section \ref{s1}, even speakers who prefer to produce (\ref{ai}a) and (\ref{ai}b) with {\em enough} can retrieve the intended interpretations of the variants without {\em enough}.} Thus, in (\ref{ai}a) and (\ref{ai}b), the prejacent is at-issue and the generalization, that the degree to which events of Sam buying a ticket the day the tickets went on sale are smart is higher than the contextual standard of {\em smart} is not at-issue. The Discourse Questions in (\ref{ai}c) and (\ref{ai}d), on the other hand, are not about the prejacent:  neither the question about B's assessment of events of Sam buying a ticket they went on sale (\ref{ai}c) nor the question of whether Sam was smart to buy a ticket the day they went on sale in (\ref{ai}d) are answered by the prejacent of B's utterances; rather they are answered by the generalization. Thus, in (\ref{ai}c) and (\ref{ai}d), the generalization is at-issue and the prejacent is not at-issue.

@@

\ex Jane saw a man with a gun. She wasn't smart to call the police. 
\end{xlist}
\end{exe}
To assess the projectivity of the prejacent, participants were asked whether the prejacent is true, e.g., `Did Sue lose her wallet?' in (\ref{cont}a), `Did Sue speak some French?' in (\ref{cont}b), and `Did Jane call the police?' in (\ref{context}a) and (\ref{context}b).\footnote{This diagnostic for projectivity differs from the `certain that' diagnostic used in the web-based corpus study or in AUTHORS 2018. Exp.~1 relied on a different diagnostic because it was run before the `certain that' diagnostic was developed. Under the assumption that participants only take the prejacent to be true if it follows from the two-sentence discourse, i.e., if the author of the two-sentence discourse is committed to the prejacent, we take the two diagnostics to be comparable in diagnosing projectivity. See AUTHORS 2018 for a discussion of additional diagnostics for projectivity.}

@@

Participants were told that they would read short descriptions of scenarios and were asked a question about each scenario. They were randomly assigned to a list and presented with the 16 stimuli, one after the other, in random order. They gave their response to the polar question on a 7-point Likert scale labeled at four points: No/1, Possibly
no/3, Possibly yes/5, Yes/7, as shown in Figure \ref{f-trial-exp1}.

@@

\paragraph{Data exclusion} The data from 5 participants who did not self-identify as native speakers of American English were excluded. 13 participants gave a response lower than 5/Possibly yes to at least one of the control stimuli in (\ref{control-exp1}a-c) or higher than 3/Possibly no \mcdm{above you have the reverse ``Possibly no/3" -- not sure which way is best, but I would use the same way throughout} to at least one of the control stimuli in (\ref{control-exp1}d-f). Their data  were also excluded, leaving data from 134 participants (ages: 18-69; mean age: 33).

@@

The target stimuli consisted of 6 pairs of three-sentence discourses like (\ref{jenny}) for each of the 10 evaluative adjectives explored in the experiments reported on in the main body of the paper, for a total of 60 pairs of target stimuli. The full set of target stimuli is provided in the GitHub repository (url, removed for anonymity). The 120 target stimuli were distributed across 12 lists of 10 stimuli each so that each adjective occurred only once per list, and each list included 5 NEASs and 5 variants with {\em enough}.

@@

\begin{enumerate}[topsep=0pt,itemsep=0pt]

@@

\begin{enumerate}[topsep=0pt,itemsep=0pt]
\item[CnT] 	Eve bought a raffle ticket. 	She	wasn't lucky	to win the first prize.
\item[CnT] 	Eve was in a car accident.	She	wasn't lucky	to get away unscathed.
\item[CnT] 	Eve wanted to be a model.	She	wasn't lucky	to have beautiful skin.
\item[CnF] 	Eve wanted to be a model.	She	wasn't lucky	to have bad skin.
\item[CnF] 	Eve bought a raffle ticket. 	She	wasn't lucky	to lose it the next day.
\item[CnF] 	Eve was in a car accident.	She	wasn't lucky	to break her neck.
\item[CxT] 	Eve has a 5th grade education.	She	wasn't lucky	to get a minimum wage job.
\item[CxT] 	Eve was a finalist in The Bachelor.	She	wasn't lucky	to be chosen.
\item[CxT] 	Eve did not understand her chemistry class.	She	wasn't lucky	to get a B.
\item[CxF] 	Eve was the best student in this class.	She	wasn't lucky	to get a B.
\item[CxF] 	Eve was called in for jury duty.	She	wasn't lucky	to be chosen.
\item[CxF] 	Eve has a first rate college education.	She	wasn't lucky	to get a minimum wage job.
